Wireless Automobile Detection, License Plate Processing, and Data Availability Network Proposal

### 2014-03-09 proposal/proposal.tex
Fixes and tweaks

1) Parking lot capacity monitoring
2) License plate detection and monitoring

@@

\subsection{Related Work}
The ACMx group at CSM has designed a system called SmartLots to track the number of vehicles in a parking lot. Their system is a wireless sensor network consisting of sensor nodes and a central base station. The sensor nodes are Arduino Fio microcomputers equipped with tri-axial magnetometors and XBEE Pro radios. The base station is one small, commercially available Raspberry Pi Linux computer. The information collected by the sensor nodes is transmitted to the base station and forwarded to a server running a small web application. The system is described in \cite{stillwell2013} and \cite{parkingWiki}. \cite{stillwell2013} describes an implementation of a system to detect automobiles entering and exiting a parking lot using the Fio and the Raspberry Pi. This system uses the ubiquitous IEEE 802.15.4 communications standard to communicate automobile detection data from the sensor nodes to the base station. \cite{parkingWiki} describes the ongoing status of the ACMx project. At the time of writing this proposal, the group has created a website that will display the status of the CTLM upper and lower lots once the monitoring system has been deployed. \cite{parkingWiki} is updated periodically with new information about project progress. The project described in this proposal will augment and extend the ACMx project while collaborating closely with Stillwell (ACMx president and author of \cite{stillwell2013}), with the goal of a real world deployment by May 2014.

@@

\begin{thebibliography}{99}
\bibitem{stillwell2013} R. Stillwell, A. Wilson ``Magnetometer Parking Sensor'' \emph{EGGN 383 Final Project, Colorado School of Mines}. December 12, 2013
\bibitem{parkingWiki}  ACMx ``Parking Sensor Wiki'' https://github.com/ColoradoSchoolOfMines/parking_sensor/wiki % Not sure how to cite this; can someone help?
\bibitem{johnson2012} X. Johnson
\end{thebibliography}

>>>>

\begin{enumerate}
\item Parking lot capacity monitoring
\item License plate detection and monitoring
\end{enumerate}

@@

\subsection{Related Work}
The ACMx group at CSM has designed a system called SmartLots to track the number of vehicles in a parking lot. Their system is a wireless sensor network consisting of sensor nodes and a central base station. The sensor nodes are Arduino Fio microcontorllers equipped with tri-axial magnetometors and XBEE Pro radios. The base station is one small, commercially available Raspberry Pi Linux computer. The information collected by the sensor nodes is transmitted to the base station and forwarded to a server running a small web application. The system is described in \cite{stillwell2013} and \cite{parkingWiki}. \cite{stillwell2013} describes an implementation of a system to detect automobiles entering and exiting a parking lot using the Fio and the Raspberry Pi. This system uses the ubiquitous IEEE 802.15.4 communications standard to communicate automobile detection data from the sensor nodes to the base station. \cite{parkingWiki} describes the ongoing status of the ACMx project. At the time of writing this proposal, the group has created a website that will display the status of the CTLM upper and lower lots once the monitoring system has been deployed. \cite{parkingWiki} is updated periodically with new information about project progress. The project described in this proposal will augment and extend the ACMx project while collaborating closely with Stillwell (ACMx president and author of \cite{stillwell2013}), with the goal of a real world deployment by May 2014.

@@

\begin{thebibliography}{99}
\bibitem{stillwell2013} R. Stillwell, A. Wilson ``Magnetometer Parking Sensor'' \emph{EGGN 383 Final Project, Colorado School of Mines}. December 12, 2013
\bibitem{parkingWiki}  ACMx ``Parking Sensor Wiki'' \begin{verbatim}https://github.com/ColoradoSchoolOfMines/parking_sensor/wiki\end{verbatim} % Not sure how to cite this; can someone help?
\bibitem{johnson2012} X. Johnson
\end{thebibliography}
